Placeholder for article 3

### 2025-01-14 analysis/paper/paper.qmd
Scatterplots for width and length of all assemblages. Plots and colours rearranged.

# Boxplot for individual measurements
# Length
solutrean_stats_length <- solutrean_stats %>%
  filter(CLASS %in% c("Flake", "ElongatedProd", "Core", "RetouchedPiece")) %>% 
  filter(LENGTH !="0" & !RMTYPE %in% c("INDET","GB","TL")) %>%
  mutate(RMTYPE = factor(RMTYPE, levels = c("TYPE 1","TYPE 2", "TYPE 3", "TYPE 4",
                                        "TYPE 5", "TYPE 6","TYPE 7", 
                                        "TYPE 8", "TYPE 9", "TYPE 10", "TYPE 11", "TL"))) %>%
  mutate(CLASS = factor(CLASS, levels = c("Flake", "ElongatedProd", "Core", "RetouchedPiece"))) %>%
  ggplot(aes(RMTYPE, LENGTH, fill = RMTYPE)) +
  geom_boxplot(aes(fill=factor(RMTYPE)), outlier.shape=21) +
  facet_wrap(~CLASS) +
  stat_summary(fun.y=mean, geom="point", shape=23) +
  labs(y="Length (mm)") +
  #coord_cartesian(ylim =  c(0, 60)) +
  scale_fill_manual(values = c("#C74B50", "#D49B54", "#911F27", "#630A10",
                              "#FACE7F", "#8B6969", "#CDAF95", "#2B4F60",
                              "#996666", "#BDD2B6", "#798777", "#BDC7C9")) +
  theme(axis.text.x=element_blank(),
        axis.ticks.x=element_blank(), axis.title.x = element_blank())
# Weight
solutrean_stats_weight <- solutrean_stats %>%
  filter(CLASS %in% c("Flake", "ElongatedProd", "Core", "RetouchedPiece")) %>% 
  filter(WEIGHT !="0" & !RMTYPE %in% c("INDET","GB","TL")) %>%
  mutate(RMTYPE = factor(RMTYPE, levels = c("TYPE 1","TYPE 2", "TYPE 3", "TYPE 4",
                                        "TYPE 5", "TYPE 6","TYPE 7", 
                                        "TYPE 8", "TYPE 9", "TYPE 10", "TYPE 11", "TL"))) %>%
  mutate(CLASS = factor(CLASS, levels = c("Flake", "ElongatedProd", "Core", "RetouchedPiece"))) %>%
  ggplot(aes(RMTYPE, WEIGHT, fill = RMTYPE)) +
  geom_boxplot(aes(fill=factor(RMTYPE)), outlier.shape=21) +
  facet_wrap(~CLASS) +
  stat_summary(fun.y=mean, geom="point", shape=23) +
  labs(y="Weight (gr)") +
  coord_cartesian(ylim =  c(0, 50)) +
  scale_fill_manual(values = c("#C74B50", "#D49B54", "#911F27", "#630A10",
                              "#FACE7F", "#8B6969", "#CDAF95", "#2B4F60",
                              "#996666", "#BDD2B6", "#798777", "#BDC7C9")) +
  theme(axis.text.x=element_blank(),
        axis.ticks.x=element_blank(), axis.title.x = element_blank())
# Width
solutrean_stats_width <- solutrean_stats %>%
  filter(CLASS %in% c("Flake", "ElongatedProd", "Core", "RetouchedPiece")) %>% 
  filter(MAXWIDTH !="0" & !RMTYPE %in% c("INDET","GB","TL")) %>%
  mutate(RMTYPE = factor(RMTYPE, levels = c("TYPE 1","TYPE 2", "TYPE 3", "TYPE 4",
                                        "TYPE 5", "TYPE 6","TYPE 7", 
                                        "TYPE 8", "TYPE 9", "TYPE 10", "TYPE 11", "TL"))) %>%
  mutate(CLASS = factor(CLASS, levels = c("Flake", "ElongatedProd", "Core", "RetouchedPiece"))) %>%
  ggplot(aes(RMTYPE, MAXWIDTH, fill = RMTYPE)) +
  geom_boxplot(aes(fill=factor(RMTYPE)), outlier.shape=21) +
  facet_wrap(~CLASS) +
  stat_summary(fun.y=mean, geom="point", shape=23) +
  labs(y="Width (mm)") +
  #coord_cartesian(ylim =  c(0, 60)) +
  scale_fill_manual(values = c("#C74B50", "#D49B54", "#911F27", "#630A10",
                              "#FACE7F", "#8B6969", "#CDAF95", "#2B4F60",
                              "#996666", "#BDD2B6", "#798777", "#BDC7C9")) +
  theme(axis.text.x=element_blank(),
        axis.ticks.x=element_blank(), axis.title.x = element_blank())

@@

# Boxplots
# Width
proto_stats_width <- proto_stats %>%
  filter(CLASS %in% c("Flake","ElongatedProd", "Core", "RetouchedPiece")) %>% 
  filter(MAXWIDTH !="0" & !RMTYPE %in% c("INDET","GB","TL")) %>%
  mutate(RMTYPE = factor(RMTYPE, levels = c("TYPE 1","TYPE 2", "TYPE 3", "TYPE 4",
                                        "TYPE 5", "TYPE 6","TYPE 7", 
                                        "TYPE 8", "TYPE 9", "TYPE 10", "TYPE 11", "TL"))) %>%
  mutate(CLASS = factor(CLASS, levels = c("Flake", "ElongatedProd", "Core", "RetouchedPiece"))) %>%
  ggplot(aes(RMTYPE, MAXWIDTH, fill = RMTYPE)) +
  geom_boxplot(aes(fill=factor(RMTYPE)), outlier.shape=21) +
  facet_wrap(~CLASS) +
  stat_summary(fun.y=mean, geom="point", shape=23) +
  labs(y="Width (mm)") +
  coord_cartesian(ylim =  c(0, 50)) +
  scale_fill_manual(values = c("#C74B50", "#D49B54", "#911F27", "#630A10",
                              "#FACE7F", "#8B6969", "#CDAF95", "#2B4F60",
                              "#996666", "#BDD2B6", "#798777", "#BDC7C9")) +
  theme(axis.text.x=element_blank(),
        axis.ticks.x=element_blank(), axis.title.x = element_blank())
# Length
proto_stats_length <- proto_stats %>%
  filter(CLASS %in% c("Flake","ElongatedProd", "Core", "RetouchedPiece")) %>% 
  filter(LENGTH !="0" & !RMTYPE %in% c("INDET","GB","TL")) %>%
  mutate(RMTYPE = factor(RMTYPE, levels = c("TYPE 1","TYPE 2", "TYPE 3", "TYPE 4",
                                        "TYPE 5", "TYPE 6","TYPE 7", 
                                        "TYPE 8", "TYPE 9", "TYPE 10", "TYPE 11", "TL"))) %>%
  mutate(CLASS = factor(CLASS, levels = c("Flake", "ElongatedProd", "Core", "RetouchedPiece"))) %>%
  ggplot(aes(RMTYPE, LENGTH, fill = RMTYPE)) +
  geom_boxplot(aes(fill=factor(RMTYPE)), outlier.shape=21) +
  facet_wrap(~CLASS) +
  stat_summary(fun.y=mean, geom="point", shape=23) +
  labs(y="Length (mm)") +
  coord_cartesian(ylim =  c(0, 60)) +
  scale_fill_manual(values = c("#C74B50", "#D49B54", "#911F27", "#630A10",
                              "#FACE7F", "#8B6969", "#CDAF95", "#2B4F60",
                              "#996666", "#BDD2B6", "#798777", "#BDC7C9")) +
  theme(axis.text.x=element_blank(),
        axis.ticks.x=element_blank(), axis.title.x = element_blank())
# Weight
proto_stats_weight <- proto_stats %>%
  filter(CLASS %in% c("Flake","ElongatedProd", "Core", "RetouchedPiece")) %>% 
  filter(WEIGHT !="0" & !RMTYPE %in% c("INDET","GB","TL")) %>%
  mutate(RMTYPE = factor(RMTYPE, levels = c("TYPE 1","TYPE 2", "TYPE 3", "TYPE 4",
                                        "TYPE 5", "TYPE 6","TYPE 7", 
                                        "TYPE 8", "TYPE 9", "TYPE 10", "TYPE 11", "TL"))) %>%
  mutate(CLASS = factor(CLASS, levels = c("Flake", "ElongatedProd", "Core", "RetouchedPiece"))) %>%
  ggplot(aes(RMTYPE, WEIGHT, fill = RMTYPE)) +
  geom_boxplot(aes(fill=factor(RMTYPE)), outlier.shape=21) +
  facet_wrap(~CLASS) +
  stat_summary(fun.y=mean, geom="point", shape=23) +
  labs(y="Weight (gr)") +
  coord_cartesian(ylim =  c(0, 50)) +
  scale_fill_manual(values = c("#C74B50", "#D49B54", "#911F27", "#630A10",
                              "#FACE7F", "#8B6969", "#CDAF95", "#2B4F60",
                              "#996666", "#BDD2B6", "#798777", "#BDC7C9")) +
  theme(axis.text.x=element_blank(),
        axis.ticks.x=element_blank(), axis.title.x = element_blank())

@@

# Boxplots
# Width
gravettian_stats_width <- gravettian_stats %>%
  filter(CLASS %in% c("Flake","ElongatedProd", "Core", "RetouchedPiece")) %>% 
  filter(MAXWIDTH !="0" & !RMTYPE %in% c("INDET","GB","TL")) %>%
  mutate(RMTYPE = factor(RMTYPE, levels = c("TYPE 1","TYPE 2", "TYPE 3", "TYPE 4",
                                        "TYPE 5", "TYPE 6","TYPE 7", 
                                        "TYPE 8", "TYPE 9", "TYPE 10", "TYPE 11", "TL"))) %>%
  mutate(CLASS = factor(CLASS, levels = c("Flake", "ElongatedProd", "Core", "RetouchedPiece"))) %>%
  ggplot(aes(RMTYPE, MAXWIDTH, fill = RMTYPE)) +
  geom_boxplot(aes(fill=factor(RMTYPE)), outlier.shape=21) +
  facet_wrap(~CLASS) +
  stat_summary(fun.y=mean, geom="point", shape=23) +
  labs(y="Width (mm)") +
  coord_cartesian(ylim =  c(0, 50)) +
  scale_fill_manual(values = c("#C74B50", "#D49B54", "#911F27", "#630A10",
                              "#FACE7F", "#8B6969", "#CDAF95", "#2B4F60",
                              "#996666", "#BDD2B6", "#798777", "#BDC7C9")) +
  theme(axis.text.x=element_blank(),
        axis.ticks.x=element_blank(), axis.title.x = element_blank())
# Length
gravettian_stats_length <- gravettian_stats %>%
  filter(CLASS %in% c("Flake","ElongatedProd", "Core", "RetouchedPiece")) %>% 
  filter(LENGTH !="0" & !RMTYPE %in% c("INDET","GB","TL")) %>%
  mutate(RMTYPE = factor(RMTYPE, levels = c("TYPE 1","TYPE 2", "TYPE 3", "TYPE 4",
                                        "TYPE 5", "TYPE 6","TYPE 7", 
                                        "TYPE 8", "TYPE 9", "TYPE 10", "TYPE 11", "TL"))) %>%
  mutate(CLASS = factor(CLASS, levels = c("Flake","ElongatedProd", "Core", "RetouchedPiece"))) %>%
  ggplot(aes(RMTYPE, LENGTH, fill = RMTYPE)) +
  geom_boxplot(aes(fill=factor(RMTYPE)), outlier.shape=21) +
  facet_wrap(~CLASS) +
  stat_summary(fun.y=mean, geom="point", shape=23) +
  labs(y="Length (mm)") +
  coord_cartesian(ylim =  c(10, 60)) +
  scale_fill_manual(values = c("#C74B50", "#D49B54", "#911F27", "#630A10",
                              "#FACE7F", "#8B6969", "#CDAF95", "#2B4F60",
                              "#996666", "#BDD2B6", "#798777", "#BDC7C9")) +
  theme(axis.text.x=element_blank(),
        axis.ticks.x=element_blank(), axis.title.x = element_blank())
# Weight
gravettian_stats_weight <- gravettian_stats %>%
  filter(CLASS %in% c("Flake","ElongatedProd", "Core", "RetouchedPiece")) %>% 
  filter(WEIGHT !="0" & !RMTYPE %in% c("INDET","GB","TL")) %>%
  mutate(RMTYPE = factor(RMTYPE, levels = c("TYPE 1","TYPE 2", "TYPE 3", "TYPE 4",
                                        "TYPE 5", "TYPE 6","TYPE 7", 
                                        "TYPE 8", "TYPE 9", "TYPE 10", "TYPE 11", "TL"))) %>%
  mutate(CLASS = factor(CLASS, levels = c("Flake","ElongatedProd", "Core", "RetouchedPiece"))) %>%
  ggplot(aes(RMTYPE, WEIGHT, fill = RMTYPE)) +
  geom_boxplot(aes(fill=factor(RMTYPE)), outlier.shape=21) +
  facet_wrap(~CLASS) +
  stat_summary(fun.y=mean, geom="point", shape=23) +
  labs(y="Weight (gr)") +
  coord_cartesian(ylim =  c(0, 60)) +
  scale_fill_manual(values = c("#C74B50", "#D49B54", "#911F27", "#630A10",
                              "#FACE7F", "#8B6969", "#CDAF95", "#2B4F60",
                              "#996666", "#BDD2B6", "#798777", "#BDC7C9")) +
  theme(axis.text.x=element_blank(),
        axis.ticks.x=element_blank(), axis.title.x = element_blank())

@@

ggpubr::ggarrange(solutrean_stats_width, solutrean_stats_length, solutrean_stats_weight, labels = c("a", "b", "c"), heights = c(5, 5, 5), ncol = 1, common.legend = TRUE, legend = "bottom")

@@

ggpubr::ggarrange(proto_stats_width, proto_stats_length, proto_stats_weight, labels = c("a", "b", "c"), heights = c(5, 5, 5), ncol = 1, common.legend = TRUE, legend = "bottom")

@@

ggpubr::ggarrange(gravettian_stats_width, gravettian_stats_length, gravettian_stats_weight, labels = c("a", "b", "c"), heights = c(5, 5, 5), ncol = 1, common.legend = TRUE, legend = "bottom")

>>>>

# Scatterplot for width and length
solutrean_scatter <- solutrean_stats |>
  filter(CLASS %in% c("Flake","ElongatedProd", "Core", "RetouchedPiece")) |>
  filter(MAXWIDTH !="0" & LENGTH != "0" & !RMTYPE %in% c("INDET","GB","TL")) |>
  dplyr::mutate(RMTYPE = case_when(
    RMTYPE == "TYPE 1" ~ "T1",
    RMTYPE == "TYPE 2" ~ "T2",
    RMTYPE == "TYPE 3" ~ "T3",
    RMTYPE == "TYPE 4" ~ "T4",
    RMTYPE == "TYPE 5" ~ "T5",
    RMTYPE == "TYPE 6" ~ "T6",
    RMTYPE == "TYPE 7" ~ "T7",
    RMTYPE == "TYPE 8" ~ "T8",
    RMTYPE == "TYPE 9" ~ "T9",
    RMTYPE == "TYPE 10" ~ "T10",
    RMTYPE == "TYPE 11" ~ "T11",
    TRUE ~ RMTYPE)) |>
   mutate(RMTYPE = factor(RMTYPE, levels = c("T1", "T2", "T3", "T4", "T5", "T6","T7", 
                                        "T8", "T9", "T10", "T11"))) |>
  mutate(CLASS = factor(CLASS, levels = c("Flake", "ElongatedProd", "Core", "RetouchedPiece"))) |>
  ggplot(aes(x = LENGTH, y = MAXWIDTH, colour = RMTYPE)) +
  geom_point(alpha = 0.9, size = 3) +
  facet_wrap(~CLASS) +
  labs(x="Length (mm)", y="Max. Width (mm") +
  scale_colour_manual(values = c("#8B7B8B", "#FFE1FF", "#EED2EE", "#D8BFD8",
                              "#CDB5CD", "#2B4F60" , "#4A708B", "#798777",
                            "#9FB6CD", "#BDD2B6", "#BDC7C9"))

# Boxplot for individual measurements
# Length
solutrean_stats_length <- solutrean_stats %>%
  filter(CLASS %in% c("Flake", "ElongatedProd", "Core", "RetouchedPiece")) %>% 
  filter(LENGTH !="0" & !RMTYPE %in% c("INDET","GB","TL")) %>%
  mutate(RMTYPE = factor(RMTYPE, levels = c("TYPE 1","TYPE 2", "TYPE 3", "TYPE 4",
                                        "TYPE 5", "TYPE 6","TYPE 7", 
                                        "TYPE 8", "TYPE 9", "TYPE 10", "TYPE 11", "TL"))) %>%
  mutate(CLASS = factor(CLASS, levels = c("Flake", "ElongatedProd", "Core", "RetouchedPiece"))) %>%
  ggplot(aes(RMTYPE, LENGTH, fill = RMTYPE)) +
  geom_boxplot(aes(fill=factor(RMTYPE)), outlier.shape=21) +
  facet_wrap(~CLASS) +
  stat_summary(fun.y=mean, geom="point", shape=23) +
  labs(y="Length (mm)") +
  #coord_cartesian(ylim =  c(0, 60)) +
  scale_fill_manual(values = c("#C74B50", "#D49B54", "#911F27", "#630A10",
                              "#FACE7F", "#8B6969", "#CDAF95", "#2B4F60",
                              "#996666", "#BDD2B6", "#798777", "#BDC7C9")) +
  theme(axis.text.x=element_blank(),
        axis.ticks.x=element_blank(), axis.title.x = element_blank())
# Weight
solutrean_stats_weight <- solutrean_stats %>%
  filter(CLASS %in% c("Flake", "ElongatedProd", "Core", "RetouchedPiece")) %>% 
  filter(WEIGHT !="0" & !RMTYPE %in% c("INDET","GB","TL")) %>%
  mutate(RMTYPE = factor(RMTYPE, levels = c("TYPE 1","TYPE 2", "TYPE 3", "TYPE 4",
                                        "TYPE 5", "TYPE 6","TYPE 7", 
                                        "TYPE 8", "TYPE 9", "TYPE 10", "TYPE 11", "TL"))) %>%
  mutate(CLASS = factor(CLASS, levels = c("Flake", "ElongatedProd", "Core", "RetouchedPiece"))) %>%
  ggplot(aes(RMTYPE, WEIGHT, fill = RMTYPE)) +
  geom_boxplot(aes(fill=factor(RMTYPE)), outlier.shape=21) +
  facet_wrap(~CLASS) +
  stat_summary(fun.y=mean, geom="point", shape=23) +
  labs(x="Raw material types" ,y="Weight (gr)") +
  coord_cartesian(ylim =  c(0, 50)) +
  scale_fill_manual(values = c("#8B7B8B", "#FFE1FF", "#EED2EE", "#D8BFD8",
                              "#CDB5CD", "#2B4F60" , "#4A708B", "#798777",
                            "#9FB6CD", "#BDD2B6", "#BDC7C9")) +
  theme(axis.text.x=element_blank(),
        axis.ticks.x=element_blank())
# Width
solutrean_stats_width <- solutrean_stats %>%
  filter(CLASS %in% c("Flake", "ElongatedProd", "Core", "RetouchedPiece")) %>% 
  filter(MAXWIDTH !="0" & !RMTYPE %in% c("INDET","GB","TL")) %>%
  mutate(RMTYPE = factor(RMTYPE, levels = c("TYPE 1","TYPE 2", "TYPE 3", "TYPE 4",
                                        "TYPE 5", "TYPE 6","TYPE 7", 
                                        "TYPE 8", "TYPE 9", "TYPE 10", "TYPE 11", "TL"))) %>%
  mutate(CLASS = factor(CLASS, levels = c("Flake", "ElongatedProd", "Core", "RetouchedPiece"))) %>%
  ggplot(aes(RMTYPE, MAXWIDTH, fill = RMTYPE)) +
  geom_boxplot(aes(fill=factor(RMTYPE)), outlier.shape=21) +
  facet_wrap(~CLASS) +
  stat_summary(fun.y=mean, geom="point", shape=23) +
  labs(y="Width (mm)") +
  #coord_cartesian(ylim =  c(0, 60)) +
  scale_fill_manual(values = c("#C74B50", "#D49B54", "#911F27", "#630A10",
                              "#FACE7F", "#8B6969", "#CDAF95", "#2B4F60",
                              "#996666", "#BDD2B6", "#798777", "#BDC7C9")) +
  theme(axis.text.x=element_blank(),
        axis.ticks.x=element_blank(), axis.title.x = element_blank())

@@

# Boxplots
# Width
proto_stats_width <- proto_stats %>%
  filter(CLASS %in% c("Flake","ElongatedProd", "Core", "RetouchedPiece")) %>% 
  filter(MAXWIDTH !="0" & !RMTYPE %in% c("INDET","GB","TL")) %>%
  mutate(RMTYPE = factor(RMTYPE, levels = c("TYPE 1","TYPE 2", "TYPE 3", "TYPE 4",
                                        "TYPE 5", "TYPE 6","TYPE 7", 
                                        "TYPE 8", "TYPE 9", "TYPE 10", "TYPE 11", "TL"))) %>%
  mutate(CLASS = factor(CLASS, levels = c("Flake", "ElongatedProd", "Core", "RetouchedPiece"))) %>%
  ggplot(aes(RMTYPE, MAXWIDTH, fill = RMTYPE)) +
  geom_boxplot(aes(fill=factor(RMTYPE)), outlier.shape=21) +
  facet_wrap(~CLASS) +
  stat_summary(fun.y=mean, geom="point", shape=23) +
  labs(y="Width (mm)") +
  coord_cartesian(ylim =  c(0, 50)) +
  scale_fill_manual(values = c("#C74B50", "#D49B54", "#911F27", "#630A10",
                              "#FACE7F", "#8B6969", "#CDAF95", "#2B4F60",
                              "#996666", "#BDD2B6", "#798777", "#BDC7C9")) +
  theme(axis.text.x=element_blank(),
        axis.ticks.x=element_blank(), axis.title.x = element_blank())

# Scatterplots for width and length
proto_scatter <- proto_stats |>
  filter(CLASS %in% c("Flake","ElongatedProd", "Core", "RetouchedPiece")) |>
  filter(MAXWIDTH !="0" & LENGTH != "0" & !RMTYPE %in% c("INDET","GB","TL")) |>
  dplyr::mutate(RMTYPE = case_when(
    RMTYPE == "TYPE 1" ~ "T1",
    RMTYPE == "TYPE 2" ~ "T2",
    RMTYPE == "TYPE 3" ~ "T3",
    RMTYPE == "TYPE 4" ~ "T4",
    RMTYPE == "TYPE 5" ~ "T5",
    RMTYPE == "TYPE 6" ~ "T6",
    RMTYPE == "TYPE 7" ~ "T7",
    RMTYPE == "TYPE 8" ~ "T8",
    RMTYPE == "TYPE 9" ~ "T9",
    RMTYPE == "TYPE 10" ~ "T10",
    TRUE ~ RMTYPE)) |>
   mutate(RMTYPE = factor(RMTYPE, levels = c("T1", "T2", "T3", "T4", "T5", "T6","T7", 
                                        "T8", "T9", "T10"))) |>
  mutate(CLASS = factor(CLASS, levels = c("Flake", "ElongatedProd", "Core", "RetouchedPiece"))) |>
  ggplot(aes(x = LENGTH, y = MAXWIDTH, colour = RMTYPE)) +
  geom_point(alpha = 0.9, size = 3) +
  facet_wrap(~CLASS) +
  labs(x="Length (mm)", y="Max. Width (mm") +
  scale_colour_manual(values = c("#8B7B8B", "#FFE1FF", "#EED2EE", "#D8BFD8",
                              "#CDB5CD", "#2B4F60" , "#4A708B", "#798777",
                            "#9FB6CD", "#BDD2B6"))

# Length
proto_stats_length <- proto_stats %>%
  filter(CLASS %in% c("Flake","ElongatedProd", "Core", "RetouchedPiece")) %>% 
  filter(LENGTH !="0" & !RMTYPE %in% c("INDET","GB","TL")) %>%
  mutate(RMTYPE = factor(RMTYPE, levels = c("TYPE 1","TYPE 2", "TYPE 3", "TYPE 4",
                                        "TYPE 5", "TYPE 6","TYPE 7", 
                                        "TYPE 8", "TYPE 9", "TYPE 10", "TYPE 11", "TL"))) %>%
  mutate(CLASS = factor(CLASS, levels = c("Flake", "ElongatedProd", "Core", "RetouchedPiece"))) %>%
  ggplot(aes(RMTYPE, LENGTH, fill = RMTYPE)) +
  geom_boxplot(aes(fill=factor(RMTYPE)), outlier.shape=21) +
  facet_wrap(~CLASS) +
  stat_summary(fun.y=mean, geom="point", shape=23) +
  labs(y="Length (mm)") +
  coord_cartesian(ylim =  c(0, 60)) +
  scale_fill_manual(values = c("#8B7B8B", "#FFE1FF", "#EED2EE", "#D8BFD8",
                              "#CDB5CD", "#2B4F60" , "#4A708B", "#798777",
                            "#9FB6CD", "#BDD2B6")) +
  theme(axis.text.x=element_blank(),
        axis.ticks.x=element_blank(), axis.title.x = element_blank())
# Weight
proto_stats_weight <- proto_stats %>%
  filter(CLASS %in% c("Flake","ElongatedProd", "Core", "RetouchedPiece")) %>% 
  filter(WEIGHT !="0" & !RMTYPE %in% c("INDET","GB","TL")) %>%
  mutate(RMTYPE = factor(RMTYPE, levels = c("TYPE 1","TYPE 2", "TYPE 3", "TYPE 4",
                                        "TYPE 5", "TYPE 6","TYPE 7", 
                                        "TYPE 8", "TYPE 9", "TYPE 10"))) %>%
  mutate(CLASS = factor(CLASS, levels = c("Flake", "ElongatedProd", "Core", "RetouchedPiece"))) %>%
  ggplot(aes(RMTYPE, WEIGHT, fill = RMTYPE)) +
  geom_boxplot(aes(fill=factor(RMTYPE)), outlier.shape=21) +
  facet_wrap(~CLASS) +
  stat_summary(fun.y=mean, geom="point", shape=23) +
  labs(x="Raw material types", y="Weight (gr)") +
  coord_cartesian(ylim =  c(0, 50)) +
  scale_fill_manual(values = c("#8B7B8B", "#FFE1FF", "#EED2EE", "#D8BFD8",
                              "#CDB5CD", "#2B4F60" , "#4A708B", "#798777",
                            "#9FB6CD", "#BDD2B6")) +
  theme(axis.text.x=element_blank(),
        axis.ticks.x=element_blank())

@@

# Scatterplots width and length
# Scatterplots for width and length
gravettian_scatter <- gravettian_stats |>
  filter(CLASS %in% c("Flake","ElongatedProd", "Core", "RetouchedPiece")) |>
  filter(MAXWIDTH !="0" & LENGTH != "0" & !RMTYPE %in% c("INDET","GB","TL")) |>
  dplyr::mutate(RMTYPE = case_when(
    RMTYPE == "TYPE 1" ~ "T1",
    RMTYPE == "TYPE 2" ~ "T2",
    RMTYPE == "TYPE 3" ~ "T3",
    RMTYPE == "TYPE 4" ~ "T4",
    RMTYPE == "TYPE 5" ~ "T5",
    RMTYPE == "TYPE 6" ~ "T6",
    RMTYPE == "TYPE 7" ~ "T7",
    RMTYPE == "TYPE 8" ~ "T8",
    RMTYPE == "TYPE 9" ~ "T9",
    RMTYPE == "TYPE 10" ~ "T10",
    TRUE ~ RMTYPE)) |>
   mutate(RMTYPE = factor(RMTYPE, levels = c("T1", "T2", "T3", "T4", "T5", "T6","T7", 
                                        "T8", "T9", "T10"))) |>
  mutate(CLASS = factor(CLASS, levels = c("Flake", "ElongatedProd", "Core", "RetouchedPiece"))) |>
  ggplot(aes(x = LENGTH, y = MAXWIDTH, colour = RMTYPE)) +
  geom_point(alpha = 0.9, size = 3) +
  facet_wrap(~CLASS) +
  labs(x="Length (mm)", y="Max. Width (mm") +
  scale_colour_manual(values = c("#8B7B8B", "#FFE1FF", "#EED2EE", "#D8BFD8",
                              "#CDB5CD", "#2B4F60" , "#4A708B", "#798777",
                            "#9FB6CD", "#BDD2B6"))

# Boxplots
# Width
gravettian_stats_width <- gravettian_stats %>%
  filter(CLASS %in% c("Flake","ElongatedProd", "Core", "RetouchedPiece")) %>% 
  filter(MAXWIDTH !="0" & !RMTYPE %in% c("INDET","GB","TL")) %>%
  mutate(RMTYPE = factor(RMTYPE, levels = c("TYPE 1","TYPE 2", "TYPE 3", "TYPE 4",
                                        "TYPE 5", "TYPE 6","TYPE 7", 
                                        "TYPE 8", "TYPE 9", "TYPE 10", "TYPE 11", "TL"))) %>%
  mutate(CLASS = factor(CLASS, levels = c("Flake", "ElongatedProd", "Core", "RetouchedPiece"))) %>%
  ggplot(aes(RMTYPE, MAXWIDTH, fill = RMTYPE)) +
  geom_boxplot(aes(fill=factor(RMTYPE)), outlier.shape=21) +
  facet_wrap(~CLASS) +
  stat_summary(fun.y=mean, geom="point", shape=23) +
  labs(y="Width (mm)") +
  coord_cartesian(ylim =  c(0, 50)) +
  scale_fill_manual(values = c("#C74B50", "#D49B54", "#911F27", "#630A10",
                              "#FACE7F", "#8B6969", "#CDAF95", "#2B4F60",
                              "#996666", "#BDD2B6", "#798777", "#BDC7C9")) +
  theme(axis.text.x=element_blank(),
        axis.ticks.x=element_blank(), axis.title.x = element_blank())
# Length
gravettian_stats_length <- gravettian_stats %>%
  filter(CLASS %in% c("Flake","ElongatedProd", "Core", "RetouchedPiece")) %>% 
  filter(LENGTH !="0" & !RMTYPE %in% c("INDET","GB","TL")) %>%
  mutate(RMTYPE = factor(RMTYPE, levels = c("TYPE 1","TYPE 2", "TYPE 3", "TYPE 4",
                                        "TYPE 5", "TYPE 6","TYPE 7", 
                                        "TYPE 8", "TYPE 9", "TYPE 10", "TYPE 11", "TL"))) %>%
  mutate(CLASS = factor(CLASS, levels = c("Flake","ElongatedProd", "Core", "RetouchedPiece"))) %>%
  ggplot(aes(RMTYPE, LENGTH, fill = RMTYPE)) +
  geom_boxplot(aes(fill=factor(RMTYPE)), outlier.shape=21) +
  facet_wrap(~CLASS) +
  stat_summary(fun.y=mean, geom="point", shape=23) +
  labs(y="Length (mm)") +
  coord_cartesian(ylim =  c(10, 60)) +
  scale_fill_manual(values = c("#C74B50", "#D49B54", "#911F27", "#630A10",
                              "#FACE7F", "#8B6969", "#CDAF95", "#2B4F60",
                              "#996666", "#BDD2B6", "#798777", "#BDC7C9")) +
  theme(axis.text.x=element_blank(),
        axis.ticks.x=element_blank(), axis.title.x = element_blank())
# Weight
gravettian_stats_weight <- gravettian_stats %>%
  filter(CLASS %in% c("Flake","ElongatedProd", "Core", "RetouchedPiece")) %>% 
  filter(WEIGHT !="0" & !RMTYPE %in% c("INDET","GB","TL")) %>%
  mutate(RMTYPE = factor(RMTYPE, levels = c("TYPE 1","TYPE 2", "TYPE 3", "TYPE 4",
                                        "TYPE 5", "TYPE 6","TYPE 7", 
                                        "TYPE 8", "TYPE 9", "TYPE 10", "TYPE 11", "TL"))) %>%
  mutate(CLASS = factor(CLASS, levels = c("Flake","ElongatedProd", "Core", "RetouchedPiece"))) %>%
  ggplot(aes(RMTYPE, WEIGHT, fill = RMTYPE)) +
  geom_boxplot(aes(fill=factor(RMTYPE)), outlier.shape=21) +
  facet_wrap(~CLASS) +
  stat_summary(fun.y=mean, geom="point", shape=23) +
  labs(x= "Raw material types", y="Weight (gr)") +
  coord_cartesian(ylim =  c(0, 60)) +
  scale_fill_manual(values = c("#8B7B8B", "#FFE1FF", "#EED2EE", "#D8BFD8",
                              "#CDB5CD", "#2B4F60" , "#4A708B", "#798777",
                            "#9FB6CD", "#BDD2B6")) +
  theme(axis.text.x=element_blank(),
        axis.ticks.x=element_blank())

@@

ggpubr::ggarrange(solutrean_scatter, solutrean_stats_weight, labels = c("a", "b"), ncol = 2, common.legend = TRUE, legend = "bottom")

@@

ggpubr::ggarrange(proto_scatter, proto_stats_weight, labels = c("a", "b"), ncol = 2, common.legend = TRUE, legend = "bottom")

@@

ggpubr::ggarrange(gravettian_scatter, gravettian_stats_weight, labels = c("a", "b"), ncol = 2, common.legend = TRUE, legend = "bottom")
